Quantifying Limits to Detection of Early Warning for Critical Transitions

### 2012-01-18 boettiger.tex
edits

  \begin{keyword}
early warning signals \sep tipping point \sep alternative stable states \sep likelihood methods 
   \end{keyword}
 \end{frontmatter}
\emph{\noindent \textbf{Running title}: Limits to Detection of Early Warning \\ 
  \textbf{Article Type}: Letter.  Abstract: 132 words, Text: 3,472 words, 34 references, 4 Figures. \\
  \textbf{Author Contributions}: C.B. wrote the software and performed the analysis with advice from A.H.  C.B. and A.H. designed the study and wrote the paper. 
}

@@

\subsection{Explicit use of the models}
Detection of warning signals as model choice (``non-parametric'' \citet{Carpenter2011e},  unpublished Dakos, Kuehn arxiv, Dakos 2011?, Gross 2011)

>>>>

  \begin{keyword}
early warning signals \sep tipping point \sep alternative stable states \sep likelihood methods 
   \end{keyword}
 \end{frontmatter}
%\emph{\noindent \textbf{Running title}: Limits to Detection of Early Warning \\ 
%  \textbf{Article Type}: Letter.  Abstract: 132 words, Text: 3,472 words, 34 references, 4 Figures. \\
%  \textbf{Author Contributions}: C.B. wrote the software and performed the analysis with advice from A.H.  C.B. and A.H. designed the study and wrote the paper. 
% }

@@

\subsection{Explicit use of the models}
Several recent approaches to early warning signals have considered fitting models, though have not considered the model-choice problem.  
Detection of warning signals as model choice (``non-parametric'' \citet{Carpenter2011e},  unpublished Dakos, Kuehn arxiv, Dakos 2011?, Gross 2011)
